Behavior Driven Development in Haskell

### 2012-05-30 paper.tex
Add a comment
adopt comment's one.

@@

We made two observations:
\begin{enumerate}
    \item
        Parts of a specification can be useful as user documentation.
    \item
        Doctest, a tool inspired by a Python module with the same
        name~\cite{doctest}, already allows to verify
        \emph{interactive examples} in Haddock comments.
\end{enumerate}

\noindent Doctest is not commonly described as a BDD tool, but we
think it fits the picture.
We show how to use Doctest and Hspec in combination to design,
document and test Haskell code.

Both, Doctest and Hspec are missing some features.  So we extend them
as needed.  In particular, our contributions are:

\begin{quote}
    \emph{kazu: I would like to change blocks above (from ``We made two ...'') with:}

@@

We will show how to use Doctest and Hspec in combination to design,
document and test Haskell code.
Both, Doctest and Hspec are missing some features.  So we extend them
as needed.  In particular, our contributions are:
\end{quote}

\begin{itemize}
\item
    We originally implemented Haskell's version of Doctest\footnote{%
    http://hackage.haskell.org/package/doctest}, and extended
    Haddock's markup to support examples, back in 2010
\item
    Add support for QuickCheck properties to Doctest and
    extend Haddock markup to support properties
    (Section
    \ref{sec:user-doc} and Section \ref{sec:doctest})

>>>>

    sol: this paragraph still has issues
    \begin{itemize}
        \item test discovery is not an aspect of BDD, but an emphasis
            on automating things, so that they e.g. work with CI is.
        \item @mkl your previous version stated, that BDD includes
            other things (ATDD!), but we only focus on TDD.  I think
            this got lost.
    \end{itemize}

@@

@@

We will show how to use Doctest and Hspec in combination to design,
document and test Haskell code.
Both, Doctest and Hspec are missing some features.  So we extend them
as needed.  In particular, our contributions are:

\begin{itemize}
\item
    We originally implemented Haskell's version of Doctest, and extended
    Haddock's markup to support examples, back in 2010
\item
    Add support for QuickCheck properties to Doctest and
    extend Haddock markup to support properties
    (Section
    \ref{sec:user-doc} and Section \ref{sec:doctest})
